---
title: "Biblioview Portal"
format: 
  dashboard:
    orientation: rows
    theme: cosmo
    nav-buttons: [github]
    github: https://github.com/tpetzoldt/biblioview
project:
  output-dir: "docs"
---

```{r}
#| context: setup
#| include: false
library(biblioview)
library(dplyr)
library(DT)

group_id <- "6605132"
api_key  <- Sys.getenv("ZOTERO_KEY")

raw_data <- fetch_all_zotero_data(group_id = group_id, api_key = api_key)
bib_data <- enrich_missing_abstracts(raw_data)
```

# Primary Library

## Sidebar {.sidebar}

### Filter Settings
Welcome to the project portal. Use the main navigation bar to switch libraries, and the global search block within the tables to perform real-time keyword lookups across titles, DOIs, and abstracts.

***

**Quick Export Actions:**
Use the copy/paste or file download controls attached directly to the active database view below.

## Row {height="100%"}

### Tabset {.tabset}

```{r}
#| html: true
callback_js <- JS(
  "table.on('click', 'td.details-control', function() {",
  "  var tr = $(this).closest('tr');",
  "  var row = table.row(tr);",
  "  if (row.child.isShown()) {",
  "    row.child.hide();",
  "    tr.removeClass('shown');",
  "  } else {",
  "    row.child(format(row.data())).show();",
  "    tr.addClass('shown');",
  "  }",
  "});",
  "function format(d) {",
  "  return '<div style=\"padding:15px; background-color:#f9f9f9; border-left:4px solid #0275d8;\">' +",
  "         '<strong>APA Citation:</strong><p>' + d[5] + '</p>' +",
  "         '<strong>Abstract:</strong><p>' + (d[6] ? d[6] : '<em>No abstract available.</em>') + '</p>' +",
  "         '</div>';",
  "}"
)
```

#### All Collections

```{r}
datatable(
  bib_data |> select(Sub_Collection, Authors, Year, Title, DOI, APA_Citation, Abstract),
  extensions = 'Buttons',
  options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel'),
    pageLength = 15,
    columnDefs = list(
      list(targets = c(5, 6), visible = FALSE)
    )
  ),
  callback = callback_js,
  escape = FALSE
)
```

#### Sub-Collection Alpha

```{r}
alpha_data <- bib_data |> filter(Sub_Collection == "Alpha")

datatable(
  alpha_data,
  extensions = 'Buttons',
  options = list(dom = 'Bfrtip', buttons = c('copy', 'csv'), pageLength=10)
)
```

# Secondary Group Library

## Row

### Alternative Group View
If your package expands to handle a completely separate Zotero Group ID down the road, it can be seamlessly assigned to this secondary page block by rendering a separate data frame object.
---
